### 2020-10-27 doc/manuscript/Dow_manuscript.Rmd
remove duplicate figure reference

#Figure numbers
schematic=1 #illustrates parameters
growth_curves_all = 2  
    rel_growth_SCBI = "2a" 
    rel_growth_HF = "2b" 
    cum_growth_SCBI = "2c" 
    cum_growth_HF = "2d" 
climwin = 3
pheno_Tsensitivity = 4
model_summary = 5
DOYtiming = 6
DOYtiming_SCBI = "6a"
DOYtiming_Harvard = "6b"

@@

model_summary_caption <- "Figure 5. (PLACEHOLDER FOR FIGURE WE DISCUSSED AT LAB MEETING)"

DOYtiming_caption <- "Figure 6. Day of year where growth milestones were achied at (a) the Smithonian Conservation Biology Institute and (b) Harvard Forest."

>>>>

#Figure numbers
schematic=1 #illustrates parameters
growth_curves_all = 2  
    rel_growth_SCBI = "2a" 
    rel_growth_HF = "2b" 
    cum_growth_SCBI = "2c" 
    cum_growth_HF = "2d" 
climwin = 3
pheno_Tsensitivity = 4
DOYtiming = 5
DOYtiming_SCBI = "5a"
DOYtiming_Harvard = "5b"

@@

DOYtiming_caption <- "Figure 5. Day of year where growth milestones were achied at (a) the Smithonian Conservation Biology Institute and (b) Harvard Forest."
